---
title: "Hw6"
author: "Apoorva Srinivasan"
date: "11/25/2018"
output: html_document
---

###Problem 1

```{r loading}
library(tidyverse)
set.seed(1)
homicide = read.csv( file = "./data/homicide-data.csv")
```

###data cleaning
```{r cleaning}
homicide= homicide%>%
  janitor::clean_names()%>%
  mutate(city_state = str_c(city, ",", state)) %>%
  subset(!city_state %in% c("Dallas,TX","Phoenix,AZ","Kansas City,MO","Tulsa,AL"))%>%
  mutate(victim_race = ifelse(victim_race != "White", "non-white", "white"))%>%
  mutate(victim_age = as.numeric(victim_age), victim_race = fct_relevel(victim_race, "white"))
```

After data cleaning, the tidy dataset consists `r nrow(homicide)` rows by `r ncol(homicide)` columns.

###Balimore glm
```{r baltimore}
Baltimore = filter(homicide, city_state == "Baltimore,MD") %>%
mutate(resolved = as.numeric(disposition == "Closed by arrest")) %>%
select(resolved, victim_age, victim_race, victim_sex)

balt_log = 
  Baltimore %>% 
  glm(resolved ~ victim_age + victim_race + victim_sex, data = ., family = binomial())%>%
  broom::tidy()%>%
  mutate(OR = exp(estimate), conf.low = exp(estimate - qnorm(0.975)*std.error), conf.high = exp(estimate + qnorm(0.975)*std.error))%>%
  filter(term == "victim_racenon-white")%>%
  select(term,OR, conf.low,conf.high)

knitr::kable(balt_log)
```

The adjusted odds ratio of solved homicides in Baltimore, MD which the victim race is non-white is 0.441 times the adjusted odds ratio of solved homicides when the victim race is white. 95% CI is between 0.312 and 0.62.

###glm for all the cities 
```{r allcities}

homicide_subset = homicide %>%
  filter(victim_race != "unknown") %>% ##removing unknown victim race
  mutate(resolved = as.numeric(disposition == "Closed by arrest"))

cities_log =
  homicide_subset %>% 
  group_by(city_state) %>% 
  nest() %>% 
  mutate(models = map(data, ~glm(resolved ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
         models = map(models, broom::tidy)) %>% 
  select(-data) %>% 
  unnest() %>%
  mutate(OR = exp(estimate), conf.low = exp(estimate - qnorm(0.975)*std.error), conf.high = exp(estimate + qnorm(0.975)*std.error)) %>%
  filter(term == "victim_racenon-white") %>%
  select(city_state,term,OR, conf.low,conf.high)

knitr::kable(cities_log)
```

###Visualization
```{r visualization}
cities_log %>%
            mutate(city_state = fct_reorder(city_state, OR))%>%
            ggplot(aes(x = city_state, y = OR))+
            geom_point()+
            geom_errorbar(aes(ymin = conf.low, ymax= conf.high))+
            theme(axis.text.x =  element_text(angle = 80))+
            labs(
              title = "The estimated OR and CIs for solving homicide comparing non-white to white victims across the U.S.",
              x = "city",
              y = "estimates and CIs"
            ) +
    theme(axis.text = element_text(size = 8))
```


From the plot above, we can see that the adjusted OR in most cities (44 out of 47) of solving homicides comparing non-white to white victims is less than 1. That is, in most cities, homicides with non-white victim are less likely to be solved than those with white victims. Also, cities with higher OR estimate tend to have wider confidence interval. For example, estimates of Durham is less precise than Boston since it's  confidence interval is much higher.


###Problem 2

```{r initial, include=FALSE}
library(broom)
library(leaps)
library(HH)
library(modelr)
library(mgcv)
```


####data loading and tidying
```{r tidy}
birthweight = read_csv("./data/birthweight.csv") %>%
  mutate(babysex = as.factor(babysex), 
         babysex = recode_factor(babysex, `1` = "Male", `2` = "Female")) %>%
  mutate(frace = as.factor(frace), 
         frace = recode_factor(frace, `1` = "White", `2` = "Black", `3` = "Asian", `4` = "Puerto Rican", `8` = "Other", `9` = "Unknown")) %>%
 mutate(mrace = as.factor(mrace),
        mrace = recode_factor(mrace, `1` = "White", `2` = "Black", `3` = "Asian", `4` = "Puerto Rican", `8` = "Other")) %>%
  mutate(malform = as.factor(malform), 
         malform = recode_factor(malform, `0` = "Absent", `1` = "Present")) 
  
###checking if there are missing values

birthweight %>% is.na() %>% sum

##There are no missing values

```

Propose a regression model for birthweight. This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.

```{r visual}

###Visualization
birthweight %>% 
  ggplot(aes(x=bwt))+
  geom_histogram()+
  labs(title="Distribution Of Childrens' Birth Weight")
```

The birthweight from the above graph is normally distributed

To build a model for birthweight, we will use backward elimication i.e start with all the predictors in stepwise/automatic approach to identify best subsets.


```{r aic}
mult_fit = lm(bwt ~ ., data=birthweight) 
step(mult_fit, direction='backward') %>% 
  broom::tidy() 
```

Given a collection of models for the data, AIC estimates the quality of each model, relative to each of the other models. We need to choose the model with smallest AIC.


The desired model is:
bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + 
    mheight + mrace + parity + ppwt + smoken

with smallest AIC of 48705.38

Hence, my model is 
```{r mymodel}
my_model = lm(bwt ~ babysex + bhead + blength + delwt + fincome +  gaweeks + mheight + parity + ppwt + smoken + mrace, data = birthweight)
summary(my_model)
```


Plotting my model residuals against fitted values 

```{r plot}
birthweight %>% 
  add_predictions(my_model) %>% 
  add_residuals(my_model) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point() + 
  geom_smooth() + 
  labs(title = "Model Residuals Against Fitted Values",
        x = "Predictions",
        y = "Residuals")
```

Comparing my model with two other suggested models:
__model_2__: using length at birth and gestational age as predictors (main effects only)

__bwt ~ blength + gaweeks__

__model_3__ : using head circumference, length, sex, and all interactions (including the three-way interaction) between these.

__bwt ~ babysex + bhead + blength + babysex*bhead + babysex*blength + bhead*blength + babysex*bhead*blength__

```{r selectingmodel}
model_2 = lm(bwt ~ blength + gaweeks, data = birthweight)
model_3 = lm(bwt ~ babysex + bhead + blength + babysex*bhead + babysex*blength + bhead*blength + babysex*bhead*blength , data = birthweight)


sum1=summary(my_model)$adj.r.squared
sum2=summary(model_2)$adj.r.squared
sum3=summary(model_3)$adj.r.squared
adj_r_squared<- matrix(c(sum1,sum2,sum3),ncol=1,byrow=TRUE)
colnames(adj_r_squared) = c("Adjusted R-squared")
rownames(adj_r_squared) = c("my_model","model_2","model_3")
adj_r_squared<- as.table(adj_r_squared)
adj_r_squared
```

My model has the highest R squared from the table above.

Comparing in terms of the cross-validated prediction error

```{r cv}
cross_validation = 
  crossv_mc(birthweight, 1000) %>%
  mutate(train = map(train, as_tibble),
         test = map(test, as_tibble)) %>% 
  mutate(my_model = map(train, ~lm(bwt ~ babysex + bhead + blength + delwt + fincome +  gaweeks + mheight + parity + ppwt + smoken + mrace, data = birthweight)),
         model_2 = map(train, ~lm(bwt ~ blength + gaweeks, data = birthweight)),
         model_3 = map(train, ~lm(bwt ~ babysex + bhead + blength + babysex*bhead + babysex*blength + bhead*blength + babysex*bhead*blength , data = birthweight)),
         rmse_1 = map2_dbl(my_model, test, ~rmse(model = .x, data = .y)),
         rmse_2 = map2_dbl(model_2, test, ~rmse(model = .x, data = .y)),
         rmse_3 = map2_dbl(model_3, test, ~rmse(model = .x, data = .y)))
```


```{r rmseplot}
rmse_plot = cross_validation %>% 
  dplyr::select(starts_with("rmse")) %>% 
  gather(key = model, value = rmse) %>% 
  mutate(model = str_replace(model, "rmse_", ""),
         model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin() + 
  labs(title="RMSE Comparisons Among Three Models")

rmse_plot
```

According to the violin plot above,the first model has lowest RMSE  among the three. Low RMSE indicates that a model  has small differences between predicted values and obseved values.Therefore, I'd pick the first model over the other two.

